Rank Verification for Exponential Families

### 2017-06-30 verifying-winner.tex
papers.bib updated

Rank verification has been studied extensively in the ranking and selection literature. See \citet{Gupta:1971wk, Gupta:1985bj} for surveys of the subset selection literature. The two main formulations of ranking and selection are closely related to procedures for multiple comparisons with the best treatment \citep{edwards1983multiple,hsu1984constrained},  but more powerful methods are available in some cases for procedures involving only the first sample rank, the problem of comparisons with the sample best; see \citet{Hsu:1996} for an overview and discussion of the relationships between these problems.

Comparisons with the sample best have been especially well-studied and the validity of Procedures 1 and 2 have been established in a different setting: balanced independent samples from log-concave location families. \citet{Gutmann:1987fk} prove the validity of Procedure 1 in this setting, and \citet{Bofinger:1991hv,Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families. \citet{Stefansson:1988wj} provide an alternative proof for the validity of Procedure 1 in the same setting, leading to a lower confidence bound analogous to that of Procedure 2; interestingly, the proof involves a very early application of the partitioning principle, later developed into fundamental technique in multiple comparisons \citep{finner2002partitioning}. These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case. Because most exponential families are not location-scale families (the Gaussian being a notable exception), and because our results involve more general dependence structures, both our proof techniques and our technical results are complementary to the techniques and results in the above works.

>>>>

Rank verification has been studied extensively in the ranking and selection literature. See \citet{Gupta:1971wk, Gupta:1985bj} for surveys of the subset selection literature. The two main formulations of ranking and selection are closely related to procedures for multiple comparisons with the best treatment \citep{Edwards:1983eo,Hsu:1984gb},  but more powerful methods are available in some cases for procedures involving only the first sample rank, the problem of comparisons with the sample best; see \citet{Hsu:1996} for an overview and discussion of the relationships between these problems.

Comparisons with the sample best have been especially well-studied and the validity of Procedures 1 and 2 have been established in a different setting: balanced independent samples from log-concave location families. \citet{Gutmann:1987fk} prove the validity of Procedure 1 in this setting, and \citet{Bofinger:1991hv,Maymin:1992fz, Karnnan:2009iv} give similar results for other models including scale and location-scale families. \citet{Stefansson:1988wj} provide an alternative proof for the validity of Procedure 1 in the same setting, leading to a lower confidence bound analogous to that of Procedure 2; interestingly, the proof involves a very early application of the partitioning principle, later developed into fundamental technique in multiple comparisons \citep{Finner:2002ju}. These results use very different technical tools than the ones we use here, require independence between the different groups (ruling out, for example, the multinomial family), and do not address the exponential family case. Because most exponential families are not location-scale families (the Gaussian being a notable exception), and because our results involve more general dependence structures, both our proof techniques and our technical results are complementary to the techniques and results in the above works.
